\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-24 WOOT/Files/experiment.tex
finish first 3 experiment

\subsection{Scripting mode}

In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13 2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as target device. 
In this experiment, \tool disguised itself as a normal keyboard and a home-brewed version of GoodUSB\cite{tian2015defending} is deployed to test the defense bypassing. We have tried to deploy the original GoodUSB on the target device, but as the GoodUSB is proposed in 2015 and the code is too outdated to run at modern OS. We have to home-brew a similar defense mechanism according to its paper.
At the beginning, our home-brewed version of GoodUSB asked victim to manually complete a CAPTCHA to  authorize the new USB device, a.k.a our \tool. But at this time, by the design of GoodUSB, our \tool can already perform limited keystroke to complete the CAPTCHA and will be rejected only after the failure of authorization. With the video feedback from \tool, the attacker successfully completes the CAPTCHA.
Up to this point, the bypass of defense like GoodUSB is completed as our \tool already gain full function from the GoodUSB and become a trusted device. Then, our \tool works similar to the original BadUSB, inserting keystroke to perform arbitrary execution on the laptop. We tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success.

\subsection{Remote control mode}

We chose \textit{iPad Pro (3rd generation)}, a tablet in iOS 14.3 with a USB Type-C interface, as the target device in this experiment.
Besides performing as normal HID devices as conventional BadUSB~\cite{badusb}, \tool could transmit real-time video streaming of screen from the target device to the attacker through WiFi or GSM.
\tool captured video from USB Type-C Hub's HDMI output via a video capture card, streamed video with \textit{FFmpeg}, a video processing utility and uploaded video stream to the attacker's device.
With a real-time video stream as an indicator, attackers can precisely control the position of mouse movements and clicks, controlling the iPad to open applications, peek at the victim's photos, etc.

Remote control mode is ideal for the attackers to control the victim's devices and grab all information shown on the victim's devices. 
However, it needs user consent for the first time and requires high power consumption to encode video streams and stable network connections.
In the real world, high power consumption will increase the possibilities of being noticed by the victim, and stable network connections is hardly guaranteed.

\subsection{Privacy extraction mode}
We chose \textit{HUAWEI P30}, a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the target device in this experiment.
As remote control mode, \tool captured video from the victim's device and use \textit{opencv} to identify valuable information from video stream. 
When the victim viewed text or photos with text, \tool used the techniques of optical character recognition (OCR) to extract text from corresponding video frames. \yechang{hyperlink to OCR?}\shuqing{I think we don't need to explain OCR nor put a reference link.}
For example, we extracted the victim's name, photo, address, and ID number when victim is viewing his/her photos of his/her ID card or passport documents,
We also extracted the victim's payment information when victim is using bank apps or payment apps.
Besides, \tool used \textit{opencv} to detect and decode QR codes or barcodes shown on the victim's device, which is expected to extract payment code information in the payment apps.
Here is an example of extracting payment code with opencv library in listing. \shuqing{Need to be modified.}\shuqing{Do we plan to add this?}

Privacy extraction mode only extracts valuable information for attackers (or highly sensitive information for victims), which is more efficient  than remote control mode.

%\begin{lstlisting}[caption={python script for extracting payment code of victim},label=lst2:qr]
%import cv2, qrcode,requests
%import pyzbar.pyzbar as pyzbar
%def decodeDisplay(video):
%    gray = cv2.cvtColor(video, cv2.COLOR_BGR2GRAY)
%    barcodes = pyzbar.decode(gray)
%    for barcode in barcodes:
%        barData = barcode.data.decode()
%        barType = barcode.type
%        requests.post('<server of attacker>',
%            data={
%                'data': barData,
%                'type': barType
%            }
%        )
%if __name__ == '__main__':
%    cam = cv2.VideoCapture(0)
%    while True:
%        ret, frame = cam.read()
%        decodeDisplay(frame)
%        if cv2.waitKey(5) == 27:
%            break
%    cam.release()
%    cv2.destroyAllWindows()
%\end{lstlisting}

\subsection{Case study}

\subsubsection{Background}

>>>>

\subsection{Scripting mode}
In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13 2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as target device. 
During this experiment, \tool disguised itself as a normal keyboard and a home-brewed version of GoodUSB\cite{tian2015defending} is deployed to test the defense bypassing. We have tried to deploy the original GoodUSB on the target device, but as the GoodUSB is proposed in 2015 and the code is too outdated to run at modern OS. We have to home-brew a similar defense mechanism according to its paper.
At the beginning, our home-brewed version of GoodUSB asked victim to manually complete a CAPTCHA to  authorize the new USB device, a.k.a our \tool. But at this time, by the design of GoodUSB, our \tool can already perform limited keystroke to complete the CAPTCHA and will be rejected only after the failure of authorization. With the video feedback from \tool, the attacker successfully completes the CAPTCHA.
Up to this point, the bypass of defense like GoodUSB is completed as our \tool already gain full function from the GoodUSB and become a trusted device. Then, our \tool works similar to the original BadUSB, inserting keystroke to perform arbitrary execution on the laptop. We tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success.

With this experiment, we have proven the defense bypassing is possible using \tool. This also warned us that we need more thorough defense against such BadUSB attack.

\subsection{Remote control mode}
To test the capability of remote control mode, we chose \textit{iPad Pro (3rd generation)}, a tablet in iOS 14.3 with a USB Type-C interface, as the target device in this experiment.
Besides disguising as normal HID devices like a conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video stream from the target device to the attacker via WiFi.
After the connection establishment, attacker performed a series actions to test the capability of \tool. At the beginning, attacker accessed album application on the iPad and obtained all the photos inside. After that, attacker tried to send messages via victim's account. At last, attacker performed a small amount of transaction using the financial application. All of these tests resulted in success and proved that \tool is a powerful attack tool.

Through this experiment, we have found that with video transmission and mouse emulation, \tool extensively expanded the attack surface of BadUSB attack, especially in mobile devices. We have archived complete hijack of victim's device in this experiment.

\subsection{Privacy extraction mode}
During the experiment of privacy extraction, we chose \textit{HUAWEI P30}, a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the target device.
In privacy extraction mode, \tool passively captured video from the victim's device and used \textit{OpenCV} to identify valuable information from video stream. 
When the victim viewed text or photos with text, \tool used the techniques of optical character recognition (OCR) to extract text from corresponding video frames.
In this experiment, attacker had successfully extracted text like name, address, ID number and other valuable personal information. We also tested the payment code extractor, which enables attacker to identify payment code in the video stream and perform transaction without password. As this is also a part of our case study, more details about the data extracted can be found in Section~\ref{subsec:case_study} and Table~\ref{table:information_extracted}.

After the experiment, we have found that as privacy extraction mode only passively process victim's video stream, this is a more power-efficient mode than remote control mode.

\subsection{Case study}
\label{subsec:case_study}
\subsubsection{Background}
